---
title: "Coding Practice"
author: "Kunpeng Yang"
date: "2/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Week 6

1. Combine the data into a single dataframe. Complete all the following exercises from the dataframe!
```{r}
# combine vectors to data frame
pirates <- data.frame("Name" = c("Astrid", "Lea", "Sarina", "Remon", "Letizia", "Babice", "Jonas", "Wendy", "Niveditha", "Gioia"),
                      "Sex" = c("F", "F", "F", "M", "F", "F", "M", "F", "F", "F"),
                      "Age" = c(30, 25, 25, 29, 22, 22, 35, 19, 32, 21),
                      "Superhero" = c("Batman", "Superman", "Batman", "Spiderman", "Batman", "Antman", "Batman", "Superman", "Maggott", "Superman"),
                      "Tattos" = c(11, 15, 12, 5, 65, 3, 9, 13, 900, 0),
                      stringsAsFactors = FALSE)
```

2. What is the median age of the 10 pirates?
```{r}
# median age
median(pirates$Age)
```

3. What was the mean age of female and male pirates separately?
```{r}
# mean age of female
female <- subset(x = pirates, subset = Sex == "F") # select entries of female and create a new frame
mean(female$Age) # calculate the mean of the column "age"

# mean age of male
male <- subset(x = pirates, subset = Sex == "M") # select entries of female and create a new frame
mean(male$Age) # calculate the mean of the column "age"
```

4. What was the most number of tattoos owned by a male pirate?
```{r}
# the most number of tattoos owned by a male pirate?
max(pirates$Tattos)
```

5. What percent of pirates under the age of 32 were female?
```{r}
under32 <- subset(x = pirates, subset = Age < 32) # select all pirates under 32
total_number = nrow(under32) # total number of pirates under 32 years old
female_number = nrow(under32[under32$Sex == "F",]) # number of rows which presents a female pirate
rate <- female_number / total_number # calculate percentage
rate
```

6. What percent of female pirates are under the age of 32?
```{r}
female <- subset(x = pirates, subset = Sex == "F") # select entries of female and create a new frame
total_female <- nrow(female) # total number of female
female_32 <- subset(x = female, subset = Age < 32) # select the females who are under 32
number_female_32 <- nrow(female_32) # number of females who are under 32
rate2 <- number_female_32 / total_female # calculate percentage
rate2
```

7. Add a new column to the dataframe called tattoos.per.year which shows how many tattoos each pirate has for each year in their life.
```{r}
pirates$tattoos.per.year <- pirates$Tattos/pirates$Age 
```

8. Which pirate had the most number of tattoos per year?
```{r}
max_tatto <- max(pirates$tattoos.per.year) # find the largest tattos per year number
pirate_max_tattos <- subset(x = pirates, subset = tattoos.per.year == max_tatto) # find the pirate 
pirate_max_tattos$Name # return the name
```

9. What are the names of the female pirates whose favorite superhero is Superman?
```{r}
like_superman <- subset(x = pirates, 
                        subset = Sex == "F" &
                                Superhero == "Superman",
                        select = Name)
like_superman
```

10. What was the median number of tattoos of pirates over the age of 20 whose favorite superhero is Spiderman?
```{r}
spiderman_20 <- subset(x = pirates,
                       subset = Sex == "M" & 
                                Superhero == "Spiderman") # find the pirates over 20 and favor Spiderman
median(spiderman_20$Tattos) # calculate the median of tatto number 
```


